Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-15 paper.qmd
Updated Figure 6 title
Updated Figure title 15

```{r}
#| label: fig-p-d-error-in-2d-two-curvy
#| fig-cap: "The $7\\text{-}D$ model error in \\gD{} layout. Color indicates square root of total error, dark blue indicating high error and light indicates low error. Most large errors are distributed near the edges of the clusters."
#| out-width: 60%
#| fig-pos: H

@@

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the MNIST digit 1 data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). All the layouts appear to be very similar. Layout c is universally poor. Layouts f that show two close clusters are universally suboptimal. Layout f is the best choice."
#| label: fig-mnist-mse
#| fig-pos: H
#| out-width: 80%

>>>>

```{r}
#| label: fig-p-d-error-in-2d-two-curvy
#| fig-cap: "The $7\\text{-}D$ model error in \\gD{} layout. Color indicates square root of total error, dark colour indicating high error and light indicates low error. Most large errors are distributed near the edges of the clusters."
#| out-width: 60%
#| fig-pos: H

@@

```{r}
#| fig-cap: "Assessing which of the 6 NLDR layouts on the MNIST digit 1 data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). All the layouts appear to be very similar. Layout c is universally poor. Layouts f that show two close clusters are universally suboptimal. Layout f is the best choice."
#| label: fig-mnist-mse
#| fig-pos: H
#| out-width: 80%
